The language of generalization: Probability, vagueness, and interaction

### 2018-03-20 paper/case1-generics.Rmd
edits to case stufy 1

Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$ (Expt. 1b).
This elicitation procedure includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure) A.
As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
4 participants were excluded for failing this trial.

@@

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
indeterminate generics were agreed with \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).

In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A).
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
We next measure the prevalence prior distribution and articulate a set of formal models that try to predict these endorsement data.

@@

There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
The property *being female* is present in almost all categories in almost exactly the same proportion, where as properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because the endorsement model makes different predictions depending on the shape of the prior.

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We do this using a Bayesian mixture model, which assumes that the data generated for each property (e.g., \textsc{lay eggs}) comes from one of two underlying Beta distributions (*Mixture of Betas*).^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs. blue lines). 
The *Single Beta* model does okay for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item.

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line.", cache = F}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

To understand the generative process of generic endorsement, we articulate a set of formal models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.
As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether referent prevalence and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.

@@

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Fig.\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
Such a model makes the wrong prediction for non-distinctive properties that in, absolute terms, have high prevalence but in relative terms, low prevalence (e.g., "Mosquitos don't carry malaria").
A simple metric like cue validity is too blunt to capture these subtleties.

@@

The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter.
The endorsement model (Eq. \ref{eq:S1}) decides whether or not to assert the generalization to a naive interpreter (Eq. \ref{eq:L0}) conditioned on a particular referent-category prevalence $p_{fk'}$  (e.g.,  the percentage of robins that lay eggs).
We use the empirically estimated referent-category prevalence (the same as used in the baseline regression model) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
The empirically measured priors from Expt. 1b are used as the literal interpreter's prevalence prior $P(p_{fk})$.

To incorporate the measurements of these model components into our endorsement model, we build a single, Bayesian joint-inference model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). 
Modeling the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
The endorsement model is then fully specified after setting the single optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burn-in.

@@

To evaluate the fixed-threshold model, we examine the posterior distribution which represents what we should believe about the latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data, as well as what predictions of the model given these parameter values.
The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].

@@

Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers context-specific $\theta$'s.
We construct the same joint-inference Bayesian data analytic model as we did for the fixed-threshold analysis; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
Thus, this model has two *fewer* parameters than the fixed-threshold model above.

We first examine the posterior predictive distribution on the prevalence prior and referent-prevalence data to ensure that the joint-inference model fits these data as well as the Bayesian model that modeled these data in isolation.
This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters.
Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1b).
This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).

The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`].

As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent prevalence*).
The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure).
It is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
The red distribution shows the $L_0$ posterior upon hearing the generic utterance that corresponding to an uncertain threshold-semantics. 
The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own distribution. 
Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are also useful things to say.
"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's distribution, despite the speaker believing that the prevalence is more than half.

@@

Generic language is the premier case study for generalizations in language. 
Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
Heretofore, however, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations, knowing when they are true and false.
Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs.

We have demonstrated that a semantics based on the probability of the feature is tenable in spite of alleged counterexamples.
The key theoretical insight is that the truth-functional semantics is *underspecified* yet still is able to formalize, using recent developments in probabilistic modeling.
Our model provides a clean delineation of world knowledge (formalized as a prior distribution) from the semantics of generalizations. 
We return to this point, and its implications for theory-building, in the general discussion.

@@

In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via our communicative model with prior knowledge about the distribution of prevalence (e.g., the prevalence of laying eggs for different kinds of animals). 
In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs. "... are female". 
However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.
We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and prevalence priors (Case 3).
In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

>>>>

We first investgate how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$.
The prevalence elicitation procedure (Expt. 1b) includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

Participants were shown thirty generic sentences in a randomized order.
They were asked to press one of two buttons (randomized between-participants) to signify whether they agreed or disagreed with the sentence (see Table 2 in Appendix for complete list). 
The thirty sentences were presented in a random order between participants and covered a range of conceptual categories described above.
Approximately 10 true, 10 false, and 10 uncertain truth-value generics were selected.
All 30 generic sentences are shown in Figure \ \@ref(fig:generics-endorsement-figure)A.
As an attention check, participants were asked at the end of the trials which button corresponded to "Agree".
4 participants were excluded for failing this trial.

@@

As a manipulation check, the first author assigned an \emph{a priori} truth-judgment (true/false/indeterminate) to each stimulus item.
As one would expect, there were substantial differences in empirical endorsements: true generics were almost universally endorsed (Maximum A-Posteriori estimate and 95\% credible interval of endorsement probability: $`r true_MAP`$ $[`r true_low`, `r true_high`]$);
indeterminate generics were agreed at a rate \emph{less} likely than chance ($`r uncertain_MAP`$ $[`r uncertain_low`, `r uncertain_high`])$) but substantially more than false generics  ($`r false_MAP`$ $[`r false_low`, `r false_high`])$).

In addition to these categorical differences between our thirty generic statements, we find a continuum of endorsement values (Figure \ \@ref(fig:generics-endorsement-figure) A). \ndg{the letters after figures are often with a space.. get rid of that?}
Such a continuum of judgments is already evidence against any theory that only predicts categorically whether a generic statement is true or false.
Ideally, a complete theory of genericity should be able to explain statements that are endorsed completely, rejected completely, and all shades in between.
We next measure the prevalence prior distribution and use them to articulate a set of quantitative models that try to predict these endorsement data.

@@

There is a lot of diversity in the shapes of the elicited prior distributions (8 examples shown in Figure\  \@ref(fig:generic-endorsement-priors-figure) A), which is roughly consistent with the schematic prior distributions used in the *Model Simulations* section (Figure \  \@ref(fig:simulations) A).
The property *being female* is present in almost all categories in almost exactly the same proportion, whereas properties such as *laying eggs* or *having spots* exhibit more structure represented by the multimodality of these distributions. 
*Being red* exists mostly at extremely low prevalence levels (i.e., 0 prevalence) but also at high prevalence levels (e.g., 50\% or 100\%), whereas *carrying malaria* is really only present at low prevalence levels.
This diversity is important because our endorsement model makes different predictions depending on the shape of the distrubution

@@

<!-- Accurately modeling the prior data is important to generate precise quantitative predictions about endorsement. -->
In order to integrate the results of this prior measurement task into our model of endorsement, we must accurately model the prior elicitation data.
We approximate the prevalence distribution for each property (e.g., \textsc{lay eggs}) with a Mixture of Betas model, which assumes that the data generated for each kind comes from one of two underlying Beta distributions.^[
  The Beta distribution is chosen because the support of this distribution is numerical values between 0 - 1, exactly the form of the response data in the prior elicitation task.
] 
We specify one of these distributions *a priori* to represent kinds of animals who *do not have* a stable causal mechanism that could give rise to the property (e.g., \textsc{lions} and \textsc{lay eggs}), which results in prevalence or prevalence values close to or equal to 0.^[
  This assumption is similar in spirit that employed by *Hurdle Models* of epidemiological data, where the observed count of zeros is often substantially greater than one would expect from standard models, such as the Poisson [e.g., when modeling adverse reactions to vaccines; @hurdleModels]
]
This "null distribution" is potentially present for all features in exactly the same way (i.e., the lack of producing the feature).
The second distribution represents kinds of animals who *do have* such a mechanism, and the two parameters of this distribution are not specified *a priori* and are not the same for all properties, but are inferred on a property-wise basis from participants' responses.
The *Mixture of Betas* distribution has a third free parameter (for each property), the relative contribution of the "null distribution" (for example: we expect the "null distribution" to not contribute at all to properties like *being female*, for which almost all categories have at least some members with the property).
To ensure the *Mixture of Betas* model of the prior is not overly complex, we fit an additional model that represents only a single underlying distribution (*Single Beta*) for a comparison.
<!-- is flexible and can represent different shapes for different properties (e.g., the differences in prevalence judgments for \textsc{lay eggs} vs. \text{has wings}). -->
For more details about model implementation and inference, see Appendix C.

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure) B; red vs. blue lines). 
The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. \ndg{but we don't use one because...?}

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prior and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line.", cache = F}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

We can now compute the predictions of our endorsement model; we first articulate a set of alternatives: models that have been previously-proposed in the literature, an alternative-form of our proposed endorsement model, and our full endorsement model.

\ndg{next two paragraphs are redundant with subsections below. delete or merge into subsections.}
As the simplest baseline hypothesis, we first explore how well referent-category prevalence itself predicts generic endorsement (e.g., does the fraction of \textsc{robins} that \textsc{lay eggs} predict the felicity of *Robins lay eggs*?).
As a secondary alternative hypothesis, we explore whether referent prevalence and *cue validity*---the probability of a kind given the feature (described in more detail below)---predicts the endorsement data.
We fit these models using standard maximum-likelihood techniques; we model uncertainty in the input measurements (i.e., referent prevalence, cue validity) by bootstrapping those data.

@@

"Robins lay eggs" and "Mosquitos don't carry malaria" highlight a shortcoming of reducing structured prevalence prior distributions to single point-estimates of cue validity.
"Lays eggs" is a somewhat diagnostic feature for *birds*, but there are many kinds of birds, and the feature is not itself diagnostic for a particular kind of bird like "Robins".
Thus, the cue validity is low even though robins are in the distinctive part of the "lays eggs" prevalence prior distribution (e.g., Fig.\ \@ref(fig:simulations)A bottom).
Furthermore, cue validity glosses over the difference between "undiagnostic" features (features present in almost every category; e.g., "not carrying malaria") and "false" features (features that are absent a particular category; e.g., "lions" and "lay eggs"; see Appendix B for more discussion of this distinction).
Such a model makes the wrong prediction for non-distinctive properties that in absolute terms have high prevalence but in relative terms low prevalence (e.g., "Mosquitos don't carry malaria").
A simple metric like cue validity is too blunt to capture these subtleties.

@@

The model we propose for endorsing generalizations is a model of an agent that decides whether or not to say the generalization to a naive interpreter.
The endorsement model (Eq. \ref{eq:S1}) decides whether or not to assert the generalization to a naive interpreter (Eq. \ref{eq:L0}) conditioned on a particular referent-category prevalence $p_{fk'}$  (e.g.,  the percentage of robins that lay eggs).
We use the empirically estimated referent-category prevalence (the same as used in the baseline regression models) as the referent-category prevalence $p_{fk'}$ in the endorsement model.
The empirical measurments of prevalence from Expt. 1b are used to constrain the literal interpreter's prevalence prior $P(p_{fk})$.

We build a single Bayesian data analysis model of the referent-category prevalence $p_{fk'}$, prevalence priors $P(p_{fk})$ (both from Expt. 1b data), and the endorsement data (Expt. 1a). \ndg{recal the mixture of betas model, and resuting params?}
Modeling the data from both Expt. 1a and 1b by a single, joint-inference model simultaneously makes explicit our assumptions about how these data were generated and is the proper way to represent the uncertainty in our measurement of the prior elicitation data (see Appendix \ndg{which one?} and Figure\  \@ref(fig:genericsModelDiagram) for further model specification details).
The endorsement model in addition has optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).
To learn about the credible values of the parameters of the model and resulting model predictions, we ran an incrementalized version of MCMC [@Ritchie2016] for 3 chains of 100,000 iterations, discarding the first 50,000 for burn-in.

@@

To evaluate the fixed-threshold model, we examine model predictions as well as the posterior distribution over latent parameters of the model (referent prevalence, prevalence priors, the optimality, fixed-threshold, and noise parameters) given the observed data.
The Maximum A-Posteriori value and 95\% highest probability density interval for the inferred (fixed) threshold and noise parameters are `r round(fixed.threshold.posterior[[1,"MAP"]], 2)` [`r round(fixed.threshold.posterior[[1,"cred_lower"]], 2)`,
`r round(fixed.threshold.posterior[[1,"cred_upper"]], 2)`] and `r round(generics.fixed.noise.posterior[[1,"MAP"]], 2)` [`r round(generics.fixed.noise.posterior[[1,"cred_lower"]], 2)`,
`r round(generics.fixed.noise.posterior[[1,"cred_upper"]], 2)`], respectively.
The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(fixed.threshold.s1opt[[1,"MAP"]], 2)` [`r round(fixed.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(fixed.threshold.s1opt[[1,"cred_upper"]], 2)`].

@@

Our underspecified threshold model is the same as the fixed-threshold model, except that rather than having a fixed $\theta$ for all contexts, the model infers context-specific $\theta$'s.
We use the same Bayesian data analysis approach; however, we are able to drop the additional parameters required for the fixed-threshold model (the fixed-threshold and noise parameters).
Thus, this model has two *fewer* parameters than the fixed-threshold model above.

We first examine the posterior predictive distribution on the prevalence prior and referent-prevalence data to ensure that the joint-inference model fits these data as well as the Bayesian model that modeled these data in isolation.
This is an important step in model validation because it tells us that our model's predictions are derived from reasonable values of the parameters.
Importantly, the model recapitulates the prior elicitation data (e.g., the probability of laying eggs among various species) and the referent-category prevalence data (e.g., the probability of laying eggs among robins) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1b).
\ndg{point to a figure or give some stat to back up thi claim?}
This result confirms that the theoretically-interesting predictions of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the prevalence distributions).

The inferred optimality parameter in Eq. \ref{eq:S1} is `r round(uncertain.threshold.s1opt[[1,"MAP"]], 2)` [`r round(uncertain.threshold.s1opt[[1,"cred_lower"]], 2)`, `r round(uncertain.threshold.s1opt[[1,"cred_upper"]], 2)`].
\ndg{this is just hanging out in space. add a sentence of interpretation, or burry it among other results.}

As we see in Figure \ \@ref(fig:generics-endorsement-figure) (top right, top right subplot), the endorsement model that uses an uncertain-threshold semantics explains nearly all of the variance in human endorsements ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.generics`$; MSE = $`r mse.gen.rsa.generics`$).
To gain some intuition for why that is the case, examine the bottom row of Figure \ref{fig:generics-endorsement-figure}.
The blue, solid lined distribution corresponds to the speaker's beliefs about the probability of the feature for the referent-category (i.e., *referent prevalence*).
The grey distribution shows the listener's prior distribution over probabilities of the feature (these are the corresponding Probability Density Functions of the Cumulative Density Functions shown in Figure \ \@ref(fig:generic-endorsement-priors-figure) ).
This prior is also the listener $L_0$'s posterior on referent prevalence upon hearing the silent utterance.
The red distribution shows the $L_0$ posterior upon hearing the generic utterance with an uncertain threshold-semantics. 
The speaker model decides when the generic utterance conveys information that would bring the listener's distribution more in line with the speaker's own beliefs. 
Thus, it finds that "Leopards have spots", "Robins lay eggs", and "Mosquitos carry malaria" are useful things to say.
"Robins are female" is neither good nor bad, as the information-content of the utterance is very small relative to silence.
"Tigers don't eat people" is rather misleading, however; it doesn't bring the listener closer to the speaker's belief, despite the speaker believing that the prevalence is more than half.

@@

Generic language is the premier case study for generalizations in language. 
Generics have been studied extensively in the cognitive and developmental psychological literatures and shown to have deep implications for wide ranging phenomena from stereotype propagation [@Rhodes2012] to motivation [@Cimpian2007].
Heretofore, no formal model has been able to pass the most basic truth-functional tests of the semantics of generalizations: knowing when they are true and false.
<!-- Determining the truth conditions is the first step towards articulating a formal theory of how the language updates beliefs. -->
We have demonstrated that a semantics based on the probability of the feature is tenable in spite of alleged counterexamples.
The key theoretical insight is that the truth-functional semantics is *underspecified* but used precisiely in context by a process of probabiistic inference.
Our model provides a clean delineation of world knowledge (formalized as a prior distribution) from the semantics of generalizations. 
We return to this point, and its implications for theory-building, in the general discussion.

@@

In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via our communicative model with prior knowledge about the distribution of prevalence (e.g., the prevalence of laying eggs for different kinds of animals). 
In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs. "... are female". 
However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.
We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case Study 2) and prevalence priors (Case Study 3).
In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.
